Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
I like this tho
Uh oops

\usepackage{listings}
\lstset{language=Java,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=true,
  commentstyle=\color{pgreen},
  keywordstyle=\color{pblue},
  numbers = left,
  stringstyle=\color{pred},
  basicstyle=\ttfamily,
  moredelim=[il][\textcolor{pgrey}]{$$},
  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
}

@@

\acmConference[ICSE 2020]{Technical Papers}{}{}

@@

\subsection{Refactoring}
In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens. There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

>>>>

\usepackage{listings}
\lstset{language=Java,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=true,
  commentstyle=\color{pgreen},
  keywordstyle=\color{pblue},
  numbers = left,
  stringstyle=\color{pred},
  basicstyle=\ttfamily,
  moredelim=[il][\textcolor{pgrey}]{\$\$},
  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
}

@@

\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}

@@

\subsection{Refactoring}
In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens. There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
